Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/qualityattributes.tex
Adding some text about SOA

\fixme{Answer question 3.3}

@@

\fixme{Answer question 3.4}

>>>>

@@

As SOA is all about standardised interfaces supplying a functionality which may be used by many different products, the areas where SOA makes sens is naturally between teh components.

Instead of creating a web-server which access a database through a specific facade, one may argue whether the desired functionality may not be generalised. "Look-up in database". This may easily be hidden behind a standardised service, e.g. a web-service, meaning that anyone on the WWW who supplies a batabase service may be used to host the beer database, and if one becomes dissatisfied with the database provider, it is transparent to simply switch to another.

Taking this one step further, perhaps the database service may be extended with a data-base type, meaning that the Beer Web Store's domain model is exposed in a service, which would allow for not only displaying ones own brands of beer, but through a discovery service, also beer-brands by other brewers on the net who implement this service. This will also point the way for a more standardised lookk-and-feel when shopping for beer.

Naturally just because a web-service (or other service) is used it does not mean that it has to be public, jet it does have some advabtages.

Finally the WS-Security web-service may be used to handle payment, and also possibly, if the database or Beer Web Store Domain model is exposed through a web-service, it may also be benificial that not everyone may have the ability to update the domain model or database, so here the WS-Security service may also come in handy.
